Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-08-31 ising/Fibonacci/about.tex

We measure charge contained within a disc. % region, circle
Commuting measurements are either disjoint discs or
one wholly contained within the other:

So (proof?) we get a basis for the Hilbert space from
a pair-of-pants (POP) decomposition:

Every surface that is not a sphere, torus, disc or annulus, has
a POP decomposition, see \cite{Ivanov01}, Theorem 2.4.A.

We say that a POP decomposition of $D_n$
{\it admits} a curve $f:L_n\to D_n$
if the curve performs a depth first traversal of $Q_n.$
This means that if the curve visits the trunk of a POP
then it visits all the legs of the POP before leaving the POP.

\important{F-moves:} given a nested POP and admissable $f$,
the f-move is the change of basis as follows:

\important{R-moves:} we examine the action of $MCG(D_n)$
on our state space. Given a single POP and curve $f:L_2\to D_n$,
the half-twist acts on $\psi$ as $R\psi$.

@@

>>>>

@@

We measure charge contained within a disc. % region, circle
Commuting measurements are either disjoint discs or
one wholly contained within the other.
So (proof?) we get a basis for the Hilbert space from
a pair-of-pants (POP) decomposition:

\begin{center}
\includegraphics[width=0.2\textwidth]{POP-1.eps}
\end{center}

The feet of the POP form the $n$ holes $Q_n$ in the disc $D$.
\footnote{Every surface that is not a sphere, torus, disc or annulus, has
a POP decomposition, see \cite{Ivanov01}, Theorem 2.4.A.}

We say that a POP decomposition of $D_n$
{\it admits} a curve $f:L_n\to D_n$
if (there is a curve in the isotopy class of)
the curve performs a depth first traversal of the POP.
This means that if the curve visits the trunk of a POP
then it visits all the legs of the POP before leaving that POP.

\begin{center}
\includegraphics[width=0.2\textwidth]{POP-2.eps}
\end{center}

\begin{center}
\includegraphics[width=0.2\textwidth]{POP-3.eps}
\end{center}

\important{F-moves:} given a nested POP and admissable $f$,
the F-move is the change of basis as follows:

\begin{center}
\includegraphics[width=0.3\textwidth]{POP-4.eps}
\end{center}

\important{R-moves:} we examine the action of $MCG(D_n)$
on our state space. Given a single POP and curve $f:L_2\to D_n$,
the half-twist on $f$ acts on $\psi$ as $R\psi$.

DIAGRAM?
